Appendix: New and simplified manual controls for projection and slice tours

### 2022-10-01 paper/appendix.Rmd
finished paragraph on visual display of slice position

The slice center, $c$, from Equation 1 in the main paper, is a point in the $p$-dimensional space. By default it is placed in the center of the data (Figure \ref{fig:anchornav} A). Moving this along a variable axis moves the slice outwards from the center of the data (Figure \ref{fig:anchornav} B, C).

>>>>

The slice center, $c$, from Equation 1 in the main paper, is a point in the $p$-dimensional space. By default, it is placed in the center of the data (Figure \ref{fig:anchornav} A). Moving this along a variable axis moves the slice outwards from the center of the data (Figure \ref{fig:anchornav} B, C). The visual display of the center position is a form of star plot as suggested useful in \textcolor{red}{REF to Catherine's paper}, where the position of the point is marked by a polygon on radial axes indicating its position relative to the variable minimum to maximum values.

### 2022-10-01 paper/appendix.tex
finished paragraph on visual display of slice position

The slice center, \(c\), from Equation 1 in the main paper, is a point
in the \(p\)-dimensional space. By default it is placed in the center of
the data (Figure \ref{fig:anchornav} A). Moving this along a variable
axis moves the slice outwards from the center of the data (Figure
\ref{fig:anchornav} B, C).

>>>>

The slice center, \(c\), from Equation 1 in the main paper, is a point
in the \(p\)-dimensional space. By default, it is placed in the center
of the data (Figure \ref{fig:anchornav} A). Moving this along a variable
axis moves the slice outwards from the center of the data (Figure
\ref{fig:anchornav} B, C). The visual display of the center position is
a form of star plot as suggested useful in
\textcolor{red}{REF to Catherine's paper}, where the position of the
point is marked by a polygon on radial axes indicating its position
relative to the variable minimum to maximum values.
